European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-21 manuscript/manuscript.qmd
Add thacker to hypotheses
start data description

>>>>

```{r}
dta <- haven::read_dta('data/panel_data.dta') 
```

This paper uses the dataset compiled by @lipscy2018, which extends the @barro2005 dataset through 2010. It provides panel data for 130 countries in five-year intervals from 1980 to 2010[^2], including information on IMF borrowing and participation outcomes, economic indicators, and measures of each country's relationship with the United States and major European powers.

[^2]: e.g. 1980-1985, 1985-1990.
